Peer-to-Peer 6502 Cellular Automata

### 2018-07-03 paper.tex
CA
abstract

\begin{abstract}
  As a toy illustration,
  this paper describes a blockchain cellular automata
  comprising a 3D array of virtual machines.
  Each machine emulates a 6502 processor with access to one page (256 bytes) of persistent storage,
  as well as the pages of its neighbors (and a read-only operating system).
  Simulation of this machine is incentivized via proof-of-work,
  writes are limited by transaction fee,
  and communications between adjacent nodes on the 3D grid are modeled as blockchain mergers.
\end{abstract}

>>>>

\begin{abstract}
  As a toy illustration,
  this paper describes a blockchain for cellular automata
  comprising a 3D array of virtual machines.
  Each machine emulates a 6502 processor with access to one page (256 bytes) of persistent storage,
  as well as the pages of its neighbors (and a read-only operating system).
  Simulation of this machine is incentivized via mining,
  writes are limited by transaction fee,
  and communications between adjacent nodes on the 3D grid are modeled as blockchain mergers.
\end{abstract}
